%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Director of Technology (Volunteer)} % Job title
  {Korean American Scientist Association - Wisconsin Chapter} % Organization
  {Madison, WI, United States} % Location
  {Dec. 2018 - Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed/Maintained NPO Chapter website and other useful IT tools for chapter management; responsible for various marketing, network activities, leadership board, and decision making.}
      \item {Project Manager \& Back-End Developer for \textbf{KSEA-Wisconsin Event Ticket System Project} (Aug. 2022 - Current)}
      \begin{itemize}
        \item {Building automated event ticket generation / admission service | Est. Release: Nov. 2022}
        \item {Send QR code with ticket information to the customers, check ticket validity and todos during admission with officers' mobile device}
        \item {Using Azure Function, Azure Blob Storage (for static website hosting), Azure Cosmos DB, CloudFlare (CDN) to minimize bandwidth, React Native}
      \end{itemize}
      \item {Project Manager \& Developer for \textbf{KSEA-Wisconsin Website Rebuilding Project} (Sep. 2019 - Nov. 2019)}
      \begin{itemize}
        \item {Built website for NPO Chapter | Led project, Collaborated with five developers | Used HTML, CSS, Jekyll, Git, Jira, MS Teams, Adobe XD}
        \item {Divided tasks for collaboration accordingly | Provided training resources and counter errors and problems during the development process}
        \item {Successfully minimized operation budget - GitHub Pages to host; used CloudFlare (CDN) to minimize bandwidth}
        \item {V2 project now launched (Est. Release: Dec. 2022) - Add admin portal, elegant design, Next.JS-powered website; Serve on MS Azure}
      \end{itemize}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Technical Lead} % Job title
  {uniQon} % Organization
  {Seoul, South Korea} % Location
  {Apr. 2020 - Oct. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Used NodeJS (TypeScript) and MongoDB to develop and operate API server, web page, and admin portal}
      \item {Elaborated idea and developed products that provide "real" college application data and mentor information to prospective applicants with their high school information, keywords from extracurricular activities, and target school lists and majors}
      \item {Closely collaborated with CEO to build concrete business plans | Trained Interns/Software Developers and engage in HR tasks}
      \item {Implemented IT infrastructure and remote working environment with Microsoft Teams, Jira, and GitHub}
      \item {Adopt Agile development workflow (Scrum) with weekly feedback to team/individuals | Traveled frequently for business meetings and recruiting}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Social Service Agent (Social Welfare)} % Job title
  {Republic of Korea Army} % Organization
  {Busan, South Korea} % Location
  {Oct. 2020 - Jul. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Served at Wonkwang Nursing Home (Long-Term Care Facilities) to complete mendatory military duty of South Korea}
    \end{cvitems}
  }

  % %---------------------------------------------------------
  % \cventry
  % {Freelance Penetration Tester} % Job title
  % {SAMSUNG Electronics} % Organization
  % {S.Korea} % Location
  % {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
  %     \item {Conducted penetration testing on SAMSUNG Smart TV.}
  %   \end{cvitems}
  %   %\begin{cvsubentries}
  %   %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
  %   %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
  %   %\end{cvsubentries}
  % }

  %---------------------------------------------------------
\end{cventries}
